\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-27 document/ms.tex
whitespace
a few typos

The \kepler\ Mission has discovered thousands of exoplanets and revolutionized
our understanding of their population.
This large, homogeneous catalog of discoveries has enabled rigorous studies of
the occurrence rate of exoplanets and planetary systems as a function of their
physical properties.
However, transit surveys like \kepler\ are most sensitive to planets with
orbital periods shorter than a few years, which is shorter than the orbital periods of
Jupiter and Saturn, which dominate the dynamics of our Solar System.
To address this deficiency, we perform a fully automated search for
long-period exoplanets with only one or two transits in the archival \kepler\
light curves.
When applied to the $\sim 40,000$ brightest Sun-like target stars, this search
produces \numcands\ long-period exoplanet candidates.
Of these candidates, 6 are novel discoveries and 5 are in systems with inner
short-period transiting planets.
Since our method involves no human intervention, we empirically characterize
the detection efficiency of our search.
Based on these results, we measure the average occurrence rate of exoplanets
smaller than Jupiter with orbital periods longer than two years to be
$2.0\pm0.7$ planets per Sun-like star.

@@

Recent work has yielded discoveries of long-period transiting planets with
only one or two transits identified in archival \kepler\ and \KT\ light curves
by visual inspection \citep{Wang:2013, Kipping:2014a, Osborn:2016,
Kipping:2016, Uehara:2016, Wang:2015}.  Detection via visual inspection requires
a high signal-to-noise for transit events to be seen by eye.
These discoveries have already yielded some tantalizing insight into the
population of long-period transiting planets.  However, as these previous results
rely on human interaction, it is prohibitively expensive to reliably measure
the completeness of these catalogs.
As a result, the existing catalogs of long-period transiting planets cannot be
used to rigorously constrain the occurrence rate of long-period planets.

@@

Using a probabilistic mass--radius relationship, we predict the masses of our
candidates and report predictions for the radial velocity amplitudes.
Unfortunately, since the target stars are faint and the amplitudes are small,
these targets are unlikely to be accessible with even the current
state-of-the-art high-precision instruments.
We also discuss the potential for astrometric follow-up using the forthcoming
data from the \gaia\ Mission with similarly discouraging results.

>>>>

The \kepler\ Mission has discovered thousands of exoplanets and revolutionized
our understanding of their population.
This large, homogeneous catalog of discoveries has enabled rigorous studies of
the occurrence rate of exoplanets and planetary systems as a function of their
physical properties.
However, transit surveys like \kepler\ are most sensitive to planets with
orbital periods much shorter than the orbital periods of Jupiter and Saturn,
the most massive planets in our Solar System.
To address this deficiency, we perform a fully automated search for
long-period exoplanets with only one or two transits in the archival \kepler\
light curves.
When applied to the $\sim 40,000$ brightest Sun-like target stars, this search
produces \numcands\ long-period exoplanet candidates.
Of these candidates, 6 are novel discoveries and 5 are in systems with inner
short-period transiting planets.
Since our method involves no human intervention, we empirically characterize
the detection efficiency of our search.
Based on these results, we measure the average occurrence rate of exoplanets
smaller than Jupiter with orbital periods in the range 2--25~years to be
$2.0\pm0.7$ planets per Sun-like star.

@@

Recent work has yielded discoveries of long-period transiting planets with
only one or two high signal-to-noise transits identified in archival \kepler\
and \KT\ light curves by visual inspection \citep{Wang:2013, Kipping:2014a,
Wang:2015, Osborn:2016, Kipping:2016, Uehara:2016}.
These discoveries have already yielded some tantalizing insight into the
population of long-period transiting planets but, since these previous results
rely on human interaction, it is prohibitively expensive to reliably measure
the completeness of these catalogs.
As a result, the existing catalogs of long-period transiting planets cannot be
used to rigorously constrain the occurrence rate of long-period planets.

@@

Using a probabilistic mass--radius relationship, we predict the masses of our
candidates and report predictions for the radial velocity semi-amplitudes.
Unfortunately, since the target stars are faint and the amplitudes are small,
these targets are unlikely to be accessible with even the current
state-of-the-art high-precision instruments.
We also discuss the potential for astrometric follow-up using the forthcoming
data from the \gaia\ Mission with similarly discouraging results.
